TBD

### 2016-08-31 paper/paper.tex
closed-loop system

\usepackage{url}                  % format URLs
\usepackage{listings}          % format code
\lstset{
  mathescape, 
  language={Java},
  basicstyle=\small
}
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   
\usepackage{graphicx}
\usepackage{float,subfig}
\usepackage{xspace,framed}
\usepackage{colortbl}
\usepackage{calc}

@@

% DOI
%\doi{10.475/123_4}

% ISBN
%\isbn{123-4567-24-567/08/06}

@@

\section{Introduction}
\section{Overview}
\section{Running Example}
\section{Program Synthesis}

@@

\begin{figure*}
\centering
\resizebox{.6\textwidth}{!}{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto,
 semithick, initial text=, ampersand replacement=\&,]

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=1cm] {
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}}; \\
   \node[fill=yellow!20] (synth) {{\sc Synthesise}};
   \&
   \node[fill=yellow!20] (verif) {{\sc Verify}}; \\
   %% \&

>>>>

\usepackage{url}                  % format URLs
\usepackage{listings}          % format code
\lstset{
  mathescape, 
  language={C},
  basicstyle=\small
}
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   
\usepackage{graphicx}
\usepackage{float,subfig}
\usepackage{xspace,framed}
\usepackage{colortbl}
\usepackage{calc}

@@

% DOI
\doi{}

% ISBN
\isbn{}

@@

\section{Introduction}

\begin{figure*}
\centering
\resizebox{.5\textwidth}{!}{
 \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
     semithick, initial text=, ampersand replacement=\&,]

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=1cm, column sep=1cm] {
   \coordinate (aux0);
   \& \node[circle] (circle) {}; 
   \& \node[fill=yellow!20] (da) {{\sc D/A}}; 
   \& \node[fill=yellow!20] (p) {{\sc P}};
   \& \node[fill=yellow!20] (ad) {{\sc A/D}}; 
   \& \coordinate (aux1);\\
   \& \coordinate (aux3); 
   \&
   \&
   \node[fill=yellow!20] (c) {C};
   \& 
   \& \coordinate (aux2);\\
  };

  \path[->] (aux0) edge (circle.west);
  \path  
   (circle.east) edge (da.west)
   (da.east) edge (p.west)
   (p.east) edge (ad.west)
   (ad.east) edge (aux1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (c.east)
   (c.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Closed Loop System. \label{fig:control}}
\end{figure*}

\section{Overview}
\section{Running Example}
\section{Program Synthesis}

@@

\begin{figure*}
\centering
\resizebox{.7\textwidth}{!}{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=1cm] {
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}}; \\
   \node[fill=yellow!20] (synth) {{\sc Synthesise}};
   \&
   \node[fill=yellow!20] (verif) {{\sc Verify}}; \\
